---
title       : mtcars dataset analysis
subtitle    : 
author      : mandelbrot
job         : coursera-devdataprod
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Deployed App

### Part0: Regression Models Course Project  
- URL: *https://github.com/mandelbrot/coursera-devdataprod-004/blob/master/shiny/www/regmods.html*
- Difference of the MPG between automatic and manual transmissions is focused in Part0.

### Part1: Shiny Application  
- URL: *http://mandelbrot.shinyapps.io/shiny/*
- A shiny-App shows the relationship between variables and miles per gallon (MPG).

### Part2: Reproducible Pitch Presentation  
- URL: *https://github.com/mandelbrot/coursera-devdataprod-004/tree/master/slidify*

### Get all SourceCode @Github:

```
git clone https://github.com/mandelbrot/coursera-devdataprod-004.git
```

## mtcars dataset - Description

### Motor Trend Car Road Tests

> The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

### Source
> Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391–411.

```{r}
library(datasets)
head(mtcars, 3)
```

---

## mtcars dataset - Format

**A data frame with 32 observations on 11 variables.**

| Index | Field | Detail |
------- | ----- | ------ |
| [, 1] | mpg | Miles/(US) gallon |
| [, 2]  | cyl | Number of cylinders |
| [, 3]  | disp | Displacement (cu.in.) |
| [, 4]  | hp | Gross horsepower |
| [, 5]	| drat | Rear axle ratio |
| [, 6]	| wt | Weight (lb/1000) |
| [, 7]	| qsec | 1/4 mile time |
| [, 8]	| vs | V/S |
| [, 9]	| am | Transmission (0 = automatic, 1 = manual) |
| [,10]	| gear | Number of forward gears |
| [,11]	| carb | Number of carburetors |

---

## Analysis - main code

See the boxplot as fig 1 for visual explanation.
```{r}
fit1 <- lm(mpg~am, data=mtcars)
summary(fit1)
```

### Finding the best model

Let's fit a model with all explanatory variables. R-squared = 0.869
```{r}
fitAll<-lm(mpg~.,mtcars)
summary(fitAll)
```

P values are high so we can use only those variables with low p values, for example p, wt, qsec and am. Actually, we got 0.8579 R-squared for model lm(mpg~hp+wt+qsec+am,mtcars) which is lower than fitAll model, but with a little experimenting, I got the following model with 0.8942 R-squared:
```{r}
fit2<-lm(mpg~hp*wt+qsec+am,mtcars)
summary(fit2)
```

### Comparing models

We got 2 models, second one combining variables describes Mpg the best.

See fig 2 and 3 for visual explanation.
```{r}
anova(fit1, fit2)

```

P value is lower than 0.05 which means that model fit2 is significant improvement over model fit1

## Appendix

### Figure 1
```{r}
m<-transform(mtcars, am=factor(am))
levels(m$am)[1] <- "Automatic"
levels(m$am)[2] <- "Manual"
plot(m$am , m$mpg, main="MPG vs Transmission", xlab="Transmission", ylab="MPG", )
abline(lm(mpg ~ am, m), col="red")
```

### Figure 2
```{r}
layout(matrix(c(1,2,3,4),2,2))
plot(fit1)
```

### Figure 3
```{r}
layout(matrix(c(1,2,3,4),2,2))
plot(fit2)
```

